\documentclass[12pt]{article}

% Set the default font
\usepackage{times}

\usepackage[utf8]{inputenc} 
\usepackage{geometry}
\geometry{a4paper, margin=0.45in}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip}

% empty the headers, footers, pagenumbers…
\pagestyle{empty}

\usepackage{tabularx}

\begin{document}
\begin{center}
    \large{\textbf{YINUO LIU}}

\end{center}

\begin{center}
    Columbus Ohio, 43215
    
    \textbf{Phone:} (+1) 984-261-5715
    
    \textbf{Email:} Yinuo.Liu@nationwidechildrens.org
\end{center}

\section{Education}
\textbf{University of North Carolina at Chapel Hill}, Chapel Hill, NC 
\hfill August 2020 - May 2024

\noindent \textbf{Bachelor of Science} in Psychology, Major GPA: 4.0
    
\noindent \textbf{Bachelor of Arts} in Computer Science, Major GPA: 4.0

\hspace{2em} Overall GPA: \textbf{3.97}

\hspace{2em} \textbf{GRE score:} Verbal: 164, Math: 170, Writing: 4.0

\section{Honors \& Awards}
\begin{itemize} [left=1em]
    \itemsep=-0.35em
    \item Karen M. Gil Internship Scholarship Recipient, 2023
    \item Dean's List, 2020 - 2024
\end{itemize}

\section{Publications}
\begin{enumerate}
    \item \textbf{Liu Y.}, Sezgin E., Youngstrom E.A. (2026). Evaluating large language models for abstract evaluation tasks: An empirical study. \textit{Frontiers in Research Metrics and Analytics}. \href{https://doi.org/10.3389/frma.2026.1807672}{doi:10.3389/frma.2026.1807672}
\end{enumerate}


\section{Manuscripts Under Review}
\begin{enumerate} [left=1em]
    \item \textbf{Liu Y.}, Bonny, A. E., \& Youngstrom, E. A. (2026). National norms and psychometrics for the Pubertal Development Scale. Preprint: \href{https://doi.org/10.64898/2026.03.25.26349307}{10.64898/2026.03.25.26349307v2}. 

    \item \textbf{Liu Y.}, Youngstrom E.A., Bondary C., Shi Z., Youngstrom J.K., Stepanova E., \& Findling R.L. (2026). Tools for helping identify behavior disorders: Comparing Bayesian nomogram and machine learning models. \textit{JAACAP OPEN}. Preprint: \href{https://osf.io/preprints/psyarxiv/4sfjz_v1}{psyarxiv}. (Revised \& Resubmitted)

    \item  \textbf{Liu Y.}, Youngstrom E.A., Elizabeth N.A., Fristad M.A. (2026). Normative benchmarks for the Parent-report Nationwide Quality of Life Scale (P-NQLS). \textit{Journal of Psychopathology and Behavioral Assessment}. Preprint:\href{https://www.medrxiv.org/content/10.64898/2026.04.16.26350886v1}{doi.org/10.64898/2026.04.16.26350886}. (Under Review)
    
    \item Youngstrom E.A., \textbf{Liu Y.}, Thompson A.J., Stephenson K., Youngstrom J.K., \& Findling R.L. (2026). Latent Profile Analysis of Parent-Reported Mood Symptoms in Youth: A Person-Centered Approach to Classification. \textit{JAACAP OPEN}. (Revised \& Resubmitted)

    \item Shi Z., Youngstrom E.A., \textbf{Liu Y.}, Youngstrom J.K., \& Findling R.L. (2026). Data Diversity vs. Model Complexity in the Prediction of Pediatric Bipolar Disorder: Evidence from Academic and Community Clinical Samples. \textit{Journal of Affective Disorders}. Preprint: \href{https://doi.org/10.64898/2026.03.26.26349447}{doi.org/10.64898/2026.03.26.26349447}. (Under Review)

    \item Youngstrom E.A., Thompson A.J., \textbf{Liu Y.}, McClellan M.B., Alcaino C., Rodda P.A., Ruch D. (2026). Measurement-Based Care Benchmarks and Bipolar Classification in ABCD Youth. \textit{JAACAP OPEN}. Preprint: \href{https://doi.org/10.64898/2026.05.06.26352558}{10.64898/2026.05.06.26352558}. (Under Review)
\end{enumerate}

\section{Book Chatpters}
\begin{enumerate} [left=1em]
    \item Yang Y., \textbf{Liu Y.}, Gonzalez M., \& Jones D.J. Delivering BPT with Under-resourced Families. \textit{Handbook for Behavioral Parent Training}. Washington, DC: American Psychological Association.
\end{enumerate}

\section{Invited Talks}
\begin{enumerate} [left=1em]
    \item \textbf{Liu Y.} (2025, November). Building ChatGPT-Based Abstract Scoring: Pilot and Application. Selected Speaker Series at Abigail Wexner Research Institute Annual Research Retreat, Columbus, OH.

    \item \textbf{Liu Y.} (2025, June). ChatGPT 101: From Theory to Practice. Presented at Institute for Mental and Behavioral Health Institute at Nationwide Children's Hospital, Columbus, OH.

    \item Youngstrom, E.A., \textbf{Liu, Y.}, \& McClellan, M. (2026, April). AI and Clinical Science in Mental and Behavioral Health: From Evidence Pipeline to Patient Outcomes. (1 hour CE). One hour seminar presented as part of the Behavioral Health Education Series in Artificial Intelligence, Nationwide Children’s Hospital, Columbus, OH.
\end{enumerate}

\section{National Presentations}
\begin{enumerate}
    \item \textbf{Liu Y.}, Bonny A., Youngstrom E.A. (2026, October). Psychometrics and Norms of Parent-Report Pubertal Development Scale in a Nationally Representative Sample [Symposium Presentation]. Part of Providing Nationally Representative Norms for Pubertal Status, Mood Symptoms, and Self-Injurious Thoughts and Behaviors. American Academy of Child and Adolescent Psychiatry (AACAP) Annual Convention, Atlanta, GA.

    \item \textbf{Liu Y.}, Youngstrom E.A. (2026, October). Integrating AI into Research Workflows: Reproducibility, Data Management, and Content Evaluation [Clinical Perspective]. Part of AI in Child and Adolescent Psychiatry: Clinical Perspectives on Current Applications and Future Directions. American Academy of Child and Adolescent Psychiatry (AACAP) Annual Convention, Atlanta, GA.

    \item \textbf{Liu Y.}, Youngstrom E.A., Fristad M.A. (2026, October). Parent Version of the Nationwide Quality of Life Scale (P-NQLS): National Norms and Psychometrics [Poster Presentation]. American Academy of Child and Adolescent Psychiatry (AACAP) Annual Convention, Atlanta, GA.
    
    \item \textbf{Liu Y.}, Youngstrom E.A., Shi Z., Youngstrom J. K., Stepanova E., \& Findling R. L. (2025, October). Predicting Oppositional Defiant Disorder: A Comparative Study of Machine Learning and Evidence-Based Decision Methods [Poster Presentation]. American Academy of Child and Adolescent Psychiatry (AACAP) Annual Convention, Chicago, IL.

    \item \textbf{Liu, Y.}, McClellan M.B., Alcaíno, C., Rodda, P.A., Youngstrom, J.K., Findling, R.L., \& Youngstrom, E.A. (2025, November). Diagnostic Accuracy of Child Mania Rating Scale for Bipolar Spectrum Disorder [Bipolar Disorders SIG Poster Exposition]. ABCT 2025 Annual Convention, New Orleans, LA, United States.

    \item Fristad, M.A., \textbf{Liu, Y.}, McClellan, M.B. \& Youngstrom, E.A. (2025, November). Examining the relationship between quality of life, mania, depression, \& suicidality in 6-11 year olds utilizing the Nationwide Norming Project [Bipolar Disorders SIG Poster Exposition]. ABCT 2025 Annual Convention, New Orleans, LA.

    \item Yang Y., \textbf{Liu Y.}, Parent Y., Jones D.J. (2024, August). Technology Enhanced Treatment: Parent Profiles Moderate Child Behavior Outcomes and Maintenance [Poster Presentation]. American Psychological Association Convention 2024, Seattle, WA.
    
    \item McClellan M.B., \textbf{Liu, Y.}, Nienaber. E.A., Alcaíno, C., Rodda, P.A., Youngstrom, J.K., Findling, R.L., \& Youngstrom, E.A. (2025, November). Reliability and Patient-Level Precision of the Full and Brief Forms of the Child Mania Rating Scale in a Large Outpatient Mental Health Sample [Bipolar Disorders SIG Poster Exposition]. ABCT 2025 Annual Convention, New Orleans, LA, United States.

    \item Youngstrom, E.A., McClellan, M., \textbf{Liu, Y.}, Fristad, M.A., Youngstrom, J.K., \& Findling, R.L. (2026, January). Advancing detection and measurement-based care of mood problems in youth: pairing normative and outpatient data. [Poster Presentation]. American College of Neuropsychopharmacology, Nassau, Bahamas.
    
    \item Yilanli M., McKay I., Waickman C.E., \textbf{Liu Y.}, Sabgir C., \& Youngstrom E.A. (2025, October). Finding the Right Scale: Analyzing Symptom Coverage in Psychosis Assessments, [Poster Presentation]. American Academy of Child and Adolescent Psychiatry (AACAP) Annual Convention, Chicago, IL.
\end{enumerate}


\section{Local Presentations}
\begin{enumerate}
    \item \textbf{Liu Y.} \& Youngstrom E.A. (2025, November). Building ChatGPT-Based Abstract Scoring: A Pilot Study for Automated Evaluation. [Poster presentation]. Abigail Wexner Research Institute Annual Research Retreat, Columbus, OH.

    \item Youngstrom E.A. \& \textbf{Liu Y.} (2025, November). Testing the Scalability of Using ChatGPT5 to Consistently Apply a Rubric as an Additional “Rater” of Scientific Abstracts. [Poster presentation]. Abigail Wexner Research Institute Annual Research Retreat, Columbus, OH.

    \item \textbf{Liu Y.}, Yilanli M., McKay I., Waickman C.E., Mondlak Z., Sabgir C., \& Youngstrom E.A.. (2025, May). Evaluating Symptom Overlap Across Psychosis Rating Scales, Poster to be presented at the EPICENTER Research Day at Ohio State University. Columbus, OH.

    \item \textbf{Liu Y.}, Gonzalez M. (2023, October). Famil-e FIRST Lab: Technology-Enhanced Helping the Non-Compliant Children, Poster to be presented at the UNC Research Fest 2023 Fall. Chapel Hill, NC.

    \item \textbf{Liu Y.}, Youngstrom J.K. (2023, November). Organizing and Updating Psychological Resources at UNC Community Clinic, Poster to be presented at Karen M. Gil Intern 2023 Fall Poster Showcase. Chapel Hill, NC.
\end{enumerate}

\section{Professional Experience}
\textbf{Clinical Research Coordinator}, full-time
\hfill Feburary 2025 - Present

\noindent\textit{Institute for Mental \& Behavioral Health Research}
\newline Nationwide Children's Hospital
\newline Director: Eric A. Youngstrom, PhD

\vspace{0.5em} \hspace{1em}
\textbf{Responsibilities:}
\begin{itemize} [left=3em]
    \itemsep=-0.35em
    \item Lead scholarly research projects across AI in research, machine learning in healthcare, and psychometrics, including study design, analysis, manuscript preparation, and publication.
    \item Develop and evaluate LLM-based research workflows, including CV screening, abstract evaluation, and AI-assisted meta-analysis pipelines.
    \item Build and maintain data analysis pipelines for scale norms, psychometric validation, machine learning models, and lab-wide research datasets.
    \item Create national norms and psychometric benchmarks for measures related to puberty, depression, mania, quality of life, and related clinical domains.
    \item Clean, score, curate, and maintain large research datasets, including BENCHMARK/YouGov data and NCH chart-review datasets, to keep them analysis-ready.
    \item Serve as a technical and psychometrics resource for lab members, supporting cross-project analyses and advising on data methods.
    \item Support RISE program coordination, grant preparation, visualization development, and monthly productivity/publication reporting.
\end{itemize}

\vspace{1em}
\noindent \textbf{Karen M. Gil Intern}, intern
\hfill August 2023 - January 2024

\noindent \textit{UNC Department of Psychology and Neuroscience Community Clinic}

\noindent Site Supervisor: Jennifer K. Youngstrom, PhD

\vspace{0.5em} \hspace{1em}
\textbf{Responsibilities:}
\begin{itemize} [left=3em]
    \itemsep=-0.35em
    \item Contacted clients to schedule phone screening and therapy sessions.
    \item Checked clinic voicemail and documented clients' contact info and medical needs.
    \item Cataloged and summarized 150+ therapy video clips for clinic trainees to review. 
    \item Updated clinic referral resource sheet with new contacts and emails.
    \item Reviewed 130 pages of clinic resource recommend and added new educational websites and videos. 
\end{itemize}

\section{Undergraduate Research Experience}
\textbf{Research Assistant}
\hfill January 2023 – May 2024

\noindent \textit{The Famil-e FIRST Lab}

\noindent University of North Carolina at Chapel Hill

\noindent Principal Investigator: Deborah Jones, PhD

\vspace{0.5em} \hspace{1em}
\textbf{Responsibilities:}
\begin{itemize} [left=3em]
    \itemsep=-0.35em
    \item Reached inter-rater reliability in coding child-directed play videos in Technology-Enhanced Helping the Non-compliant Children (TE-HNC) Program and coded 20 videos for parent treatment outcomes.
    \item Shadowed Behavioral Parent Training practicum and received training in intervention skills.
    \item Logged in inter-rater reliability data of therapists delivering HNC sessions.
\end{itemize}

\vspace{1em}
\noindent \textbf{Research Assistant}
\hfill July 2022 – May 2023

\noindent \textit{Brain and Early Experience Study}

\noindent University of North Carolina at Chapel Hill

\noindent Principal Investigator: Cathi Propper, PhD

\vspace{1em} \hspace{1em}
\textbf{Responsibilities:}
\begin{itemize} [left=3em]
    \itemsep=-0.35em
    \item Contacted participant families and scheduled lab visits via phone calls and emails.
    \item Administered 25 times of child behavior assessment to 30-month children and performed the “Stranger Task” (roleplaying a stranger to test for child’s social interactions).
    \item Edited and segmented Actigraphy data of 6-month children to label sleep/activity periods and calculate average sleep time.
    \item Prepared bio-sample kits and collected samples from children and parents (hair, saliva).
\end{itemize}

\section{Skills}
\begin{itemize}
    \itemsep=-.3em
    \item \textbf{Programming Languages:} Python, Java, C, JavaScript, HTML, Structured Query Language 
    \item \textbf{Statistics and Questionnaire Software:} R, MPlus, SPSS, Qualtrics, SAS
    \item \textbf{Productivity Tools:} Word, Excel, PowerPoint, Canvas, LateX
\end{itemize}


\end{document}

